### 2015-01-28 src/paper2/paper2.tex
Update figure captions

	\caption{(A) Top-view illustrating three key events within the experiment. Left panel: At the extreme right position, the reference target (R) is flashed. Middle panel: The participant moves while keeping fixation on the fixation point (FP). Right panel: At the left most position, one of the probe locations (P) is flashed. (B) Timing of key events. Within a run of sinusoidal sled motion, participants always fixated the fixation point. At the rightmost point, the reference (R) was flashed for 50 \si{\milli\second}. Then, at the extreme left position, a probe (P) was shown for 50 \si{\milli\second}. Participants responded whether the probe was presented to the left or right of the reference using a joystick. (C) Locations of fixation points (plus signs) and reference/probe locations (bars) used in our experiment (see also \tabref{p2:tab1}).}

@@

    \caption{Performance in one subject (S1). The proportion of rightward responses is plotted against probe location relative to the reference. Size of a data point represents the number of trials tested. Solid lines, best-fit cumulative Gaussians, characterized by bias (l) and standard deviation (r). (A) Constant reference depth, variable fixation depth, 150 \si{\milli\metre} translation. (B) Constant reference depth, variable fixation depth, 300 \si{\milli\metre} translation. (C) Variable reference depth, constant fixation depth, 150 \si{\milli\metre} translation. (D) Variable reference depth, constant fixation depth, 300 \si{\milli\metre}  translation.}

@@

    \caption{Top view of the updating biases ($\mu$). Dots, individual bias values; error bars, averages (\textpm SD) across participants; +, fixation point. (A), (B), (C), (D): Conditions as in Figure \ref{p2:fig2}.}

@@

    \caption{Head- versus gaze-centered effects in updating bias (l). (A) Average bias (6 SE) across participants plotted against head- centric version angle of fixation point, for each of the 16 conditions. (B) Same data plotted as a function of head-centric angle to the reference location. (C) Same data plotted against the gaze-centric location of the reference target. Open symbols, 150 mm translation. Closed symbols, 300 mm translation. Circles, constant fixation depth. Squares, constant reference depth. Color scheme as in Figure \ref{p2:fig1}C.}

>>>>

	\caption{\panelref{A} Top-view illustrating three key events within the experiment. Left panel: At the extreme right position, the reference target (R) is flashed. Middle panel: The participant moves while keeping fixation on the fixation point (FP). Right panel: At the left most position, one of the probe locations (P) is flashed. \panelref{B} Timing of key events. Within a run of sinusoidal sled motion, participants always fixated the fixation point. At the rightmost point, the reference (R) was flashed for 50 \si{\milli\second}. Then, at the extreme left position, a probe (P) was shown for 50 \si{\milli\second}. Participants responded whether the probe was presented to the left or right of the reference using a joystick. \panelref{C} Locations of fixation points (plus signs) and reference/probe locations (bars) used in our experiment (see also \tabref{p2:tab1}).}

@@

    \caption{Performance in one subject (S1). The proportion of rightward responses is plotted against probe location relative to the reference. Size of a data point represents the number of trials tested. Solid lines, best-fit cumulative Gaussians, characterized by bias (l) and standard deviation (r). \panelref{A} Constant reference depth, variable fixation depth, 150 \si{\milli\metre} translation. \panelref{B} Constant reference depth, variable fixation depth, 300 \si{\milli\metre} translation. \panelref{C} Variable reference depth, constant fixation depth, 150 \si{\milli\metre} translation. \panelref{D} Variable reference depth, constant fixation depth, 300 \si{\milli\metre}  translation.}

@@

    \caption{Top view of the updating biases ($\mu$). Dots, individual bias values; error bars, averages (\textpm SD) across participants; +, fixation point. \panelref{A} to \panelref{D}: Conditions as in Figure \ref{p2:fig2}.}

@@

    \caption{Head- versus gaze-centered effects in updating bias (l). \panelref{A} Average bias (6 SE) across participants plotted against head- centric version angle of fixation point, for each of the 16 conditions. \panelref{B} Same data plotted as a function of head-centric angle to the reference location. \panelref{C} Same data plotted against the gaze-centric location of the reference target. Open symbols, 150 mm translation. Closed symbols, 300 mm translation. Circles, constant fixation depth. Squares, constant reference depth. Color scheme as in Figure \ref{p2:fig1}C.}

### 2015-01-28 src/paper4/p4_results.tex
Updated papers
Update figure captions

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/paper4/paper4_figure2.eps}

    \caption{A. Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference movements. B. [Need to decide what to put here.]}
    \label{p4:fig2}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/paper4/paper4_figure3.eps}

	\caption{Psychometric curves (colored lines) and associated binned data (circles) for one participant. Circle size represents the amount of trials within the bin. Psychometric curves before collapsing across reference order are shown as gray lines. A.  Body-fixed condition while fixation was either near (brown) or far (orange). B. World-fixed condition while fixation was either near (purple) or far (pink).}
	\label{p4:fig3}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/paper4/paper4_figure4.eps}

	\caption{PSEs for all participants and the average \textpm SE. A.  Body-fixed condition while fixation was either near (brown) or far (orange). B. World-fixed condition while fixation was either near (purple) or far (pink).}
	\label{p4:fig4}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/paper4/paper4_figure5.eps}

	\caption{}
	\label{p4:fig5}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/paper4/p4_figure2.pdf}

    \caption{\panelref{A} Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference movements. \panelref{B} [Need to decide what to put here.]}
    \label{p4:fig2}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/paper4/p4_figure3.pdf}

	\caption{\panelref{A} and \panelref{B} Psychometric curves (colored lines) and associated binned data (circles) for one participant. Circle size represents the amount of trials within the bin. Psychometric curves before collapsing across reference order are shown as gray lines. \panelref{A} Body-fixed condition (brown) while fixation was either near (dark) or far (light). \panelref{B} World-fixed condition (purple) while fixation was either near (dark) or far (light).
	\panelref{C} and \panelref{D} Individual and average points of subjective equality (PSEs). Color scheme matches panels A. and B.
	}
	\label{p4:fig3}
\end{figure}

@@

\begin{wrapfigure}{l}[5pt]{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{src/paper4/p4_figure4.pdf}

	\caption{PSEs for all participants and the average \textpm SE. \panelref{A}  Body-fixed condition while fixation was either near (brown) or far (orange). \panelref{B} World-fixed condition while fixation was either near (purple) or far (pink).}
	\label{p4:fig4}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}[5pt]{0.5\textwidth}
    \includegraphics[width=1.0\textwidth]{src/paper4/p4_figure5.pdf}

	\caption{}
	\label{p4:fig5}
\end{wrapfigure}
